### 2020-06-28 abstract.tex
abs+parial intro

\begin{abstract}
\label{abstract}
We use smartphones everywhere and privacy concerns have arisen for ``shoulder surfing'', where strangers peek at our phone in public areas. This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technique, we believe that this threat is underestimated as a malicious attacker can peek from farther away with the assist of his smartphone camera and SR algorithms. To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing, including an unique multi-image SR neural network architecture designed for commercial smartphones. Evaluation demonstrates its efficiency and robustness, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range in different scenarios only using multiple blurred images. And it outperforms other known SR algorithms and fills the blank space of multi-image SR for shoulder surfing attack.
\end{abstract}

>>>>

\begin{abstract}
\label{abstract}
We use smartphones everywhere and privacy concerns have arisen for the ``shoulder surfing'' attack, where strangers peek at our phone in public areas. To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his smartphone camera and SR algorithms, rendering the underestimated threat model. To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including an unique deep neural network (DNN) architecture for multi-image SR. Evaluation demonstrates its efficiency and robustness, allowing a human to read 95\% of the multiple types of contents off a smartphone screen at 1.5m range in different scenarios only using multiple blurred images. And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.
\end{abstract}

### 2020-06-28 design.tex
abs+parial intro

\section{Design}
\label{sec-design}

\subsection{network design}

The core of the \textsf{SRPeek} system is a specially designed multi-frame SR neural network, accepting a group of $N$ images indexed $x_1^{(0)}$ to $x_N^{(0)}$ as input and generating an image with higher resolution $y$ as output. The network comprises $L$ layers, each of which implements a non-linear transformation $H_l(\cdot)$, where $l$ indexes the layer. As mentioned before, in each layer images are processed separately, with the merging layers as a revenue for communication, so that the output of each layer is correspondent to the input.  We denote the output of the $l^{th}$ layer as $x_1^{(l)}$ to $x_N^{(l)}$, which is also the input of the $(l+1)^{th}$ layer. Till now the model is not different from traditional SR models:

@@

The full structure of a 3 layer network is shown in Fig~\ref{fig-system}.

@@

\item Processing. As our network accepts only 9x9 patches, we will iteratively process all the overlapping 9x9 boxes among the input photo. For example, a 10x10 image will be four 9x9 patches, and a 11x11 image nine patches, etc(see fig.~\ref{fig-patches}. After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. When all patches are processed, their outputs are merged together. The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result. In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.

@@

These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds. At critical times requiring continuous monitoring so as not to miss transient display, e.g. password entering, the system can simply lengthen the input phase across that period and process the data afterwards. The workflow of our system is shown in fig.~\ref{fig-workflow}.
\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/workflow.pdf}
    \caption{Illustration of the workflow of our shoulder-surfing system.}
    \label{fig-workflow}
\end{figure}

>>>>

\section{System Design}
\label{sec-design}

\subsection{network design}
The core of the \textsf{SRPeek} system is a specially designed multi-frame SR neural network, accepting a group of $N$ images indexed $x_1^{(0)}$ to $x_N^{(0)}$ as input and generating an image with higher resolution $y$ as output. The network comprises $L$ layers, each of which implements a non-linear transformation $H_l(\cdot)$, where $l$ indexes the layer. As mentioned before, in each layer images are processed separately, with the merging layers as a revenue for communication, so that the output of each layer is correspondent to the input.  We denote the output of the $l^{th}$ layer as $x_1^{(l)}$ to $x_N^{(l)}$, which is also the input of the $(l+1)^{th}$ layer. Till now the model is not different from traditional SR models:

@@

The full structure of a 3 layer network is shown in Figure~\ref{fig-system}.

@@

\item Processing. As our network accepts only 9x9 patches, we will iteratively process all the overlapping 9x9 boxes among the input photo. For example, a 10x10 image will be four 9x9 patches, and a 11x11 image nine patches, etc(see Figure~\ref{fig-patches}. After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. When all patches are processed, their outputs are merged together. The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result. In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.

@@

These steps are repeatedly executed to enable the attacker to monitor the victim at an interval of a few seconds. At critical times requiring continuous monitoring so as not to miss transient display, e.g. password entering, the system can simply lengthen the input phase across that period and process the data afterwards. The workflow of our system is shown in Figure~\ref{fig-workflow}.

### 2020-06-28 evaluation.tex
abs+parial intro

 
\section{Model Evaluation}
We evaluate the ability of the network model, testing its performance in different training and testing conditions. We perform the following experiments with two phones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras, the telephoto camera(which we use in the experiments) possessing up to 5x optical zooming ability which we will utilize fully in our experiments. 
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Fig~\ref{fig-control} and Fig.~\ref{fig-control2}). Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lenses(without optical zoom) is trained and tested at 1~2 meters range, while the one with optical zoom at 5~7.5 meters, at which distance less than 5\% of the characters(only the simplist ones) can be recognized by humans from the photos without the assistance of SR algorithms. The model can achieve an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
In the optical zoom group the accuracy of the model dropped drastically at 7m distance. Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes,etc.). It's the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixelwize error rises steadily with the increased distance, the accuracy will experience a drastic drop.

@@

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
    \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
    \label{fig-control2}
\end{figure}
\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Fig.~\ref{fig-random} and Fig.~\ref{fig-random2}). The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.

@@

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Fig.~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.

@@

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level averageing. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing. The results are shown in Fig.~\ref{table-comp}.

@@

\section{System Evaluation}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it's insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1~2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Fig.~\ref{table-accuracy}.

@@

\subsection{Influence of hand tremors}
We ask 5 participants to capture images with handheld smartphones, keeping their hand still to their greatest effort(Handheld camera). We process these images and let them read the results. We compare this performance to the data collected on stationary phones to evaluate the influence of hand tremors.
We also ask participants to hold a smartphone in their hands and read a piece of text, without other additional instructions(Handheld target). The user may freely interact with the phone when reading. We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Fig.~\ref{table-tremor}.

@@

\subsection{Perceived shoulder surfing susceptibility}
We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenario. The attacker will be sitting or standing behind the participant at 1.5m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP. None of the participants were alerted by the attacker's behavior and reported suspicion of shoulder-surfing. We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.
\section{Limitations}
\subsection{Image Capturing Ability}
Latest models of smartphones can capture images at 10 frames per second in burst mode easily, however, this ability is not common in phones that are 3 years old. Heavily used phones also performs less than ideal when capturing images in burst mode. Also, when capturing images the user need to hold their phone as still as possible to avoid motion blur and assist image alignment. The user also has to keep a sharp focus on the target phone.
\subsection{Processing Ability}
To achieve best performance the user needs a phone with strong processing capabilities to run the neural network at real time. As neural networks have been common place in numerous modern APPs, most phones of the latest generation have upgraded their processing ability to run neural networks, but older versions might not possess such processing powers and cannot process images at real-time.
\subsection{Motion and Tremors}
In our experiment we assume the observed user will hold still his/hers phone, and not making interactions too often. However some users may tilt their phones during interactions—especially when typing with one hand. Too much tremor will cause motion blur in captured images and misalignment between frames, thus degrading the result.

>>>>

 
\section{Model Evaluation}
We evaluate the ability of the network model, testing its performance in different training and testing conditions. We perform the following experiments with two phones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras, the telephoto camera(which we use in the experiments) possessing up to 5x optical zooming ability which we will utilize fully in our experiments. 
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Figure~\ref{fig-control} and Figure~\ref{fig-control2}). Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lenses(without optical zoom) is trained and tested at 1~2 meters range, while the one with optical zoom at 5~7.5 meters, at which distance less than 5\% of the characters(only the simplist ones) can be recognized by humans from the photos without the assistance of SR algorithms. The model can achieve an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
In the optical zoom group the accuracy of the model dropped drastically at 7m distance. Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes,etc.). It's the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixelwize error rises steadily with the increased distance, the accuracy will experience a drastic drop.

@@

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
    \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
    \label{fig-control2}
\end{figure}
\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random} and Figure~\ref{fig-random2}). The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.

@@

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Figure~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.

@@

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level averageing. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing. The results are shown in Figure~\ref{table-comp}.

@@

\section{System Evaluation}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it's insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1~2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Figure~\ref{table-accuracy}.

@@

\subsection{Influence of hand tremors}
We ask 5 participants to capture images with handheld smartphones, keeping their hand still to their greatest effort(Handheld camera). We process these images and let them read the results. We compare this performance to the data collected on stationary phones to evaluate the influence of hand tremors.
We also ask participants to hold a smartphone in their hands and read a piece of text, without other additional instructions(Handheld target). The user may freely interact with the phone when reading. We capture images of the phone at the same time to see how our system deal with a moving target screen.The results are shown in Figure~\ref{table-tremor}.

@@

\subsection{Perceived shoulder surfing susceptibility}
We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenario. The attacker will be sitting or standing behind the participant at 1.5m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP. None of the participants were alerted by the attacker's behavior and reported suspicion of shoulder-surfing. We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.

### 2020-06-28 implementation.tex
abs+parial intro

The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network. We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset. Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model with a set of training images captured from it. When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours). There are no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data. %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in fig.~\ref{fig-training}), but our system works perfectly without it.
 Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Fig~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset. However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Fig~\ref{fig-train-single-4}).
 \begin{figure}
     \centering
     \subfigure[input from same environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1.png}
         \label{fig-train-single-1}
         }
     \subfigure[output of (a)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2.png}
         \label{fig-train-single-2}
         }
     \subfigure[input from different environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5.png}
         \label{fig-train-single-3}
         }
     \subfigure[output of (c)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4.png}
         \label{fig-train-single-4}
         }
     \subfigure[ground truth]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
         \label{fig-train-single-5}
         }
        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
        \label{fig-train-single}
\end{figure}

>>>>

The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network. We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset. Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model with a set of training images captured from it. When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours). There are no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data. %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.
 Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Figure~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset. However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Figure~\ref{fig-train-single-4}).
 \begin{figure}
     \centering
     \subfigure[input from same environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1.png}
         \label{fig-train-single-1}
         }
     \subfigure[output of (a)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2.png}
         \label{fig-train-single-2}
         }
     \subfigure[input from different environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5.png}
         \label{fig-train-single-3}
         }
     \subfigure[output of (c)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4.png}
         \label{fig-train-single-4}
         }
     \subfigure[ground truth]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
         \label{fig-train-single-5}
         }
        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
        \label{fig-train-single}
\end{figure}
